Select-based random access \\ to variable-byte encodings

### 2020-04-28 gradu/msc_english_contents.tex
Adds more text

 - TODO: introduce each chapter briefly

@@

The following example decompresses first four values from Figure~\ref{bris_ds} and assumes the maximum length of integers to be 4 blocks. Array $P$ is used to store the block indices. Initially $P$ = 
[-1,-1,-1,-1], where -1 denotes that the value is unset and that level has not been reached yet. The start of the subarray is index 0. $P$[0] is -1, which means the value is unset. Because the $rank$ method 
does not need an actual $rank$ call in the first block array, $P$[1] = 0 and that value is used to fetch the first block. $B_1$[0] shows that the element is continued to the next block level. $P$[1] is also -1, 
so $P$[1] = $rank_0$($B_1$,0) is used to fetch the second block. $B_2$[0] indicates that the element is not continued anymore.

Currently $P$ is [0,0,-1,-1]. The location of the first block of the next element is fetched by increasing $P$[0] by 1 and then using the incremented value. The bit array shows that this element is only 
one block long. The first two blocks of the third element is fetched the same way. $P$[2] is unset, so $P$[2] = $rank_0$($B_2$,0) is used for the third block, which is the last block of that element. After 
these elements, $P$ is [2,1,0,-1]. The index locations of the fourth element are fetched from $P$ the same way. In the end $P$ is [3,2,0,-1] and the process could continue if needed.

@@

\end{tikzpicture}
\caption{TODO this}\label{bris_subarray}

@@

 - TODO: does this need a picture?

 - TODO: is referring to Figure~\ref{bris_ds} enough or should this part have another image of the (maybe different) block setup

 - TODO: is the explanation unclear?

>>>>

@@

An example situation from a previous chapter is pictured in Figure~\ref{bris_subarray}. A subarray of four elements will be decoded from the start of the array. The starting location could very well be 
anything, but the start was chosen for simplicity. The array $P$ is used to store the block indices. Initially the values in $P$ are set to -1 to denote that the value is unset and that level has not been 
reached yet. When a block level is queried for the first time, the index value from the $rank$ call is stored in $P$ and used instead of further $rank$ calls.

The subarray is in this case started from index 0. The value of $P$ for the current level is checked at the start of every block fetch. $P$[1] is unset, so a value needs to fetched and stored there. Because 
the $rank$ method does not need an actual $rank$ call in the first block array, $P$[1] is set to the starting index 0 and that value is used to fetch the first block. $B_1$[0] shows that the element is 
continued to the next block level. $P$[2] is -1 (because this is the first time the second level is reached), so a $P$[2] = $rank_0$($B_1$,0) call is needed to fetch the second block. $B_2$[0] indicates 
that the element is not continued anymore.

For the location of the first block of the second element, $P[1]$ is checked. It is set, so the value it contains is increased by one and used as the index. The bit array shows that this element is only 
one block long. The first two blocks of the third element are fetched the same way. $P$[2] is unset and a  $P$[2] = $rank_0$($B_2$,0) is used to fetch the index. The fourth element does not reach to a new 
block level, so each block location is fetched from $P$.

@@

\end{tikzpicture}
\caption{Index lookup array demonstration in $rank$ based subarray query}\label{bris_subarray}

@@
